Supplemental Materials

### 2021-06-18 supplement/supplement-main.Rmd
prettied graphs

@@

@@

# z$nodes_df
z$nodes_df <- z$nodes_df %>% mutate(label = recode_nodes(label))
z$nodes_df$fontname <- "Helvetica"
z$nodes_df$shape <- "ellipse"
# z$nodes_df$fillcolor <- ifelse(z$nodes_df$id==13, "grey","white")
z$nodes_df$fixedsize <- FALSE
z$edges_df$penwidth <- abs(edge_df_mod$value)*2
z$edges_df$penwidth <- 1.5
# z$edges_df$label <- round(edge_df_mod$value,2)
# z$edges_df$color <- ifelse(edge_df_mod$value > 0, "blue","red")
z$edges_df$color <- map_to_brewer(edge_df_mod$value, option="RdBu")

@@

z2 <- custom_plot.HydeNetwork(h2)
boot_res %>%
  filter(direction>0, strength>.2) %>% 
  # filter(parameter!="phi",parameter!="w_leak") %>%
  # rename(from = parameter) %>%
  # mutate(from = gsub("w_","",from)) %>%
  select(to, from, strength) %>%
  merge(z2$nodes_df %>% rename(from = label) %>% select(id, from), by="from") %>%
  mutate(from = id) %>%
  select(-id) %>%
  merge(z2$nodes_df %>% rename(to = label) %>% select(id, to), by="to") %>%
  mutate(to = id) %>%
  arrange(to,from) -> edge_df_mod

@@

@@

@@

@@

df_demo <- s1_demo %>% 
  bind_rows(
    s2_demo %>% 
      select(workerId, age, sex, race, religion, educ, income, parent) %>% 
      mutate(
        study = "2",
        )
  ) %>% 
  bind_rows(
    s3_demo %>% 
      mutate(
        study = paste0("3",study),
        sex = ifelse(sex=="female","Female","Male")
        ) %>% 
      select(workerId, age, sex, race, religion, educ, income, parent, study)
  ) %>% 
  bind_rows(
    s1_demo %>% 
      filter(workerId %in% s4_wide$workerId) %>% 
      mutate(study = "4")
  ) %>% 
  mutate(
    race = ordered(race,
                   levels = c(
                          "White",
                          "Black or African American",
                          "Hispanic/Latino",
                          "Hawaiian or PI",
                          "Asian",
                          "Native American",
                          "Other or prefer not to say"
                          )
                   ),
    educ = ordered(educ,
                   levels = c(
                          "No Diploma",
                          "High School",
                          "Some Undergraduate",
                          "Undergraduate Degree",
                          "Some Graduate",
                          "Graduate Degree",
                          "Doctorate",
                          "Prefer not to say"
                          )
                   ),
    income = ordered(income,
                     levels = c(
                          "Less than $20,000",
                          "$20,000 - $30,000",
                          "$30,001 - $50,000",
                          "$50,001 - $70,000",
                          "$70,001 - $100,000",
                          "More than $100,000",
                          "Prefer not to say"
                          )
                     )

  ) %>% 
  mutate(
    age = ifelse(age < 18,NA,age),
    income = str_replace_all(income, "\\$",""),
    study = paste("Study", study)
    )

@@

# and create big table with table1 and t1kable()
# trying wrapping with factor() to get it to print integer counts
demographics_tbl <- table1::table1(~ factor(sex) + age + factor(race) + factor(religion) + factor(educ) + factor(income) + factor(parent)  | study, data=df_demo)

table1::t1kable(demographics_tbl) %>% 
  kable_classic(latex_options="scale_down")

>>>>

z2 <- custom_plot.HydeNetwork(h2)
boot_res %>%
  filter(direction>0, strength>.2) %>% 
  # filter(parameter!="phi",parameter!="w_leak") %>%
  # rename(from = parameter) %>%
  # mutate(from = gsub("w_","",from)) %>%
  mutate(strength = strength*direction) %>% 
  select(to, from, strength) %>%
  merge(z2$nodes_df %>% rename(from = label) %>% select(id, from), by="from") %>%
  mutate(from = id) %>%
  select(-id) %>%
  merge(z2$nodes_df %>% rename(to = label) %>% select(id, to), by="to") %>%
  mutate(to = id) %>%
  arrange(to,from) -> edge_df_mod

@@

```{r}
boot_df <- boot_res %>% filter(strength>.2, direction>0)
```

@@

# z$nodes_df
z$nodes_df <- z$nodes_df %>% mutate(label = recode_nodes(label))
z$nodes_df$fontname <- "Helvetica"
z$nodes_df$shape <- "ellipse"
# z$nodes_df$fillcolor <- ifelse(z$nodes_df$id==13, "grey","white")
z$nodes_df$fixedsize <- FALSE
z$edges_df$penwidth <- abs(edge_df_mod$value)*2
z$edges_df$penwidth <- 1.5
z$edges_df$label <- round(edge_df_mod$value,2)
# z$edges_df$color <- ifelse(edge_df_mod$value > 0, "blue","red")
z$edges_df$color <- map_to_brewer(edge_df_mod$value, option="RdBu")

@@

@@

```{r echo=F, fig.width=8, fig.height=4}
## combined plot for paper
library(patchwork)

s2_diff_plot <- s2_scored %>% 
  spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_nodes2(scale),
    condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
    ) %>% 
  group_by(condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition)) +
  geom_pointrange(position=position_dodge(width=.25)) +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  scale_color_manual(values=c("#0067b1","#c50024")) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.35,.9),
    legend.direction = "horizontal",
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", color="Intervention")

obs_pred <- make_pred_df(s2_mdf, base_model, "diseaseSevere")

s2_obs_pred_plot <- obs_pred %>% # a bit of a hack
  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
  geom_errorbar( width=0, color="grey") +
  geom_point(size=2.5) +
  annotate(geom="text", x=.03, y=-.04, label= paste("r =", cor_val)) +
  coord_cartesian(xlim=c(-.06,.06), ylim=c(-.06,.06)) +
  theme_bw(base_size=11) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(aspect.ratio = 1) +
  labs(title = "B", y = "Observed change", x="Predicted change")

s2_diff_plot + s2_obs_pred_plot + plot_layout(ncol=2, widths = c(2,1))
```

@@

```{r fig.width=8, fig.height=4}
s3_diff_plot <- s3_scored %>% 
  # spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_nodes2(scale),
    condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
    ) %>% 
  group_by(condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition)) +
  geom_pointrange(position=position_dodge(width=.25)) +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  scale_color_manual(values=c("#0067b1","#c50024")) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.6,.15),
    legend.direction = "horizontal",
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", color="Intervention")

obs_pred <- make_pred_df(s3_mdf, base_model, "vaccTox")

s3_obs_pred_plot <- obs_pred %>% 
  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
  geom_point(size=2.5) +
  geom_errorbar(alpha=.5, width=0) +
  # coord_fixed(ratio=1) +
  coord_cartesian(xlim=c(-.12,.08), ylim=c(-.12,.08)) +
  annotate(geom="text", x=.05, y=-.1, label= paste("r =", cor_val)) +
  theme_bw(base_size=11) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(aspect.ratio = 1) +
  labs(title = "B", y = "Observed change", x="Predicted change")

s3_diff_plot + s3_obs_pred_plot + plot_layout(ncol=2, widths = c(2,1))
```

@@

```{r fig.width=8, fig.height=4}
s4_diff_plot <- combined %>% 
  filter(returned==TRUE, !is.na(vacc_news)) %>% # somehow 5? participants slippd by without answering 
  mutate(diff = posttest-pretest) %>%
  mutate(
    vacc_news = as.factor(vacc_news),
    scale = recode_nodes2(scale)
    ) %>%
  group_by(vacc_news,scale) %>%
  summarize(
    mean = mean(diff),
    se = sd(diff)/sqrt(n()),
    ul = mean + se,
    ll = mean - se,
    ul95 = mean + 1.96*se,
    ll95 = mean - 1.96*se
  ) %>%
  ungroup() %>%
  mutate(vacc_news = factor(vacc_news, c(1,0), labels=c("Yes","No"))) %>%
  # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
  ggplot(aes(x=reorder(scale, mean), y = mean, ymin =ll, ymax=ul, color=vacc_news)) +
  geom_point(position=position_dodge(width=.25), size=2, shape=16) +
  geom_errorbar(position=position_dodge(width=.25), width=0, alpha=.8) +
  # geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
  geom_hline(yintercept = 0, linetype="dashed",alpha=.5) +
  scale_color_manual(values=c("#0067b1","#c50024")) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.35,.85),
    legend.direction = "horizontal",
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", color="News Exposure")

s4_obs_pred_plot <- obs_pred %>% # a bit of a hack
  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
  geom_point(size=2.5) +
  geom_errorbar(alpha=.5, width=0) +
  annotate(geom="text", x=.04, y=-.04, label= paste("r =", cor_val)) +
  coord_cartesian(xlim=c(-.07,.06), ylim=c(-.07,.06)) +
  theme_bw(base_size=11) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(aspect.ratio = 1) +
  labs(title = "B", y = "Observed change", x="Predicted change")

s4_diff_plot + s4_obs_pred_plot + plot_layout(ncol=2, widths = c(2,1))
```

@@

df_demo <- s1_demo %>% 
  bind_rows(
    s2_demo %>% 
      select(workerId, age, sex, race, religion, educ, income, parent) %>% 
      mutate(
        study = "2",
        )
  ) %>% 
  bind_rows(
    s3_demo %>% 
      mutate(
        study = paste0("3",study),
        sex = ifelse(sex=="female","Female","Male")
        ) %>% 
      select(workerId, age, sex, race, religion, educ, income, parent, study)
  ) %>% 
  bind_rows(
    s1_demo %>% 
      filter(workerId %in% s4_wide$workerId) %>% 
      mutate(study = "4")
  ) %>% 
  mutate(
    race = ordered(race,
                   levels = c(
                          "White",
                          "Black or African American",
                          "Hispanic/Latino",
                          "Hawaiian or PI",
                          "Asian",
                          "Native American",
                          "Other or prefer not to say"
                          )
                   ),
    educ = ordered(educ,
                   levels = c(
                          "No Diploma",
                          "High School",
                          "Some Undergraduate",
                          "Undergraduate Degree",
                          "Some Graduate",
                          "Graduate Degree",
                          "Doctorate",
                          "Prefer not to say"
                          )
                   ),
    income = str_replace_all(income, "\\$",""),
    income = ordered(income,
                     levels = c(
                          "Less than 20,000",
                          "20,000 - 30,000",
                          "30,001 - 50,000",
                          "50,001 - 70,000",
                          "70,001 - 100,000",
                          "More than 100,000",
                          "Prefer not to say"
                          )
                     )

  ) %>%
  mutate(
    age = ifelse(age < 18,NA,age),
    # income = str_replace_all(income, "\\$",""),
    study = paste("Study", study)
    )

@@

# and create big table with table1 and t1kable()
# trying wrapping with factor() to get it to print integer counts
# demographics_tbl <- table1::table1(~ factor(sex) + age + factor(race) + factor(religion) + factor(educ) + factor(income) + factor(parent)  | study, data=df_demo)

demographics_tbl <- table1::table1(~ sex + age + race + religion + educ+ income + parent  | study, data=df_demo)

table1::t1kable(demographics_tbl, booktabs = T) %>% 
  kable_classic(latex_options="scale_down")
